Effects of masked prime duration in an online lexical decision task

### 2021-03-08 Manuscript.Rmd
Begin method

b) allowing the non-decision parameter T_er to vary as a function of the priming conditions for word stimuli should improve the model (compared to a model that has only one T_er parameter for all word stimuli regardless of priming condition).

@@

b) allowing the non-decision parameter T_er to vary as a function of the priming conditions for word stimuli should improve the model compared to a model that has only one T_er parameter for all word stimuli regardless of priming condition.

@@

# Method

@@

## Participants

## Material

## Procedure

## Data analysis

@@

# Results

# Discussion

>>>>

b)  allowing the non-decision parameter $T_{er}$ to vary as a function of the priming conditions for word stimuli should improve the model (compared to a model that has only one $T_{er}$ parameter for all word stimuli regardless of priming condition).

@@

b)  allowing the non-decision parameter $T_{er}$ to vary as a function of the priming conditions for word stimuli should improve the model compared to a model that has only one $T_{er}$ parameter for all word stimuli regardless of priming condition.

@@

# Experiment 1

In the first experiment, we tested whether we could observe reliable effects of masked priming at prime durations of 33 ms and 50 ms (roughly corresponding to two and three frames at a refresh rate of 60 Hz).

@@

## Method

```{r load_exp1_data, message=FALSE, echo=FALSE}
library(tidyverse)
library(sp)
library(rworldmap)

e1_all_participants <- read_csv("participant_data_exp1.csv")

e1 <- read_csv(file = "Exp 1 data.csv")

e1_actual_participants <- filter(e1_all_participants, PROLIFIC_PID %in% e1$participant & `What is your age?` != 99)

participant_ages <- e1_actual_participants$`What is your age?`

male_participants_nr <- filter(e1_actual_participants, `What is your gender (optional)?` == "Male") %>% nrow

female_participants_nr <- filter(e1_actual_participants, `What is your gender (optional)?` == "Female") %>% nrow

other_participants_nr <- filter(e1_actual_participants, `What is your gender (optional)?` == "Other") %>% nrow

NA_participants_nr <- filter(e1_actual_participants, `What is your gender (optional)?` == "Other") %>% nrow
```

### Participants

We collected data from `r e1_actual_participants$PROLIFIC_PID %>% unique %>% length` participants aged from `r participant_ages %>% min` to `r participant_ages %>% max` (mean age: `r participant_ages %>% mean %>% round(2)`) recruited through Prolific [www.prolific.co, -@prolific2021]. Of the participants, The experiment was only be shown to participants who have indicated that English is their first language in the Prolific screening questions. They were paid £1.25 for their participation (corresponding to £5/hour). Participants indicated that English was their first language before starting the experiment.

### Material

### Procedure

### Data analysis

@@

## Results

## Discussion

# General Discussion

### 2021-03-08 Manuscript.tex
Begin method

\begin{enumerate}
\def\labelenumi{\alph{enumi})}
\item
  the drift rate parameter for words to vary as a function of the priming condition should not improve the model (compared to a model that has a single drift rate parameter for all word stimuli regardless of priming condition) , while
\item
  allowing the non-decision parameter T\_er to vary as a function of the priming conditions for word stimuli should improve the model (compared to a model that has only one T\_er parameter for all word stimuli regardless of priming condition).
\end{enumerate}

@@

\begin{enumerate}
\def\labelenumi{\alph{enumi})}
\item
  allowing the drift rate parameter for words to vary as a function of the priming condition should improve the model compared to a model that has a single drift rate parameter for all word stimuli regardless of priming condition, and
\item
  allowing the non-decision parameter T\_er to vary as a function of the priming conditions for word stimuli should improve the model compared to a model that has only one T\_er parameter for all word stimuli regardless of priming condition.
\end{enumerate}

@@

\hypertarget{method}{%
\section{Method}\label{method}}

@@

\hypertarget{participants}{%
\subsection{Participants}\label{participants}}

\hypertarget{material}{%
\subsection{Material}\label{material}}

\hypertarget{procedure}{%
\subsection{Procedure}\label{procedure}}

\hypertarget{data-analysis}{%
\subsection{Data analysis}\label{data-analysis}}

@@

\hypertarget{results}{%
\section{Results}\label{results}}

\hypertarget{discussion}{%
\section{Discussion}\label{discussion}}

@@

>>>>

\begin{enumerate}
\def\labelenumi{\alph{enumi})}
\item
  the drift rate parameter for words to vary as a function of the priming condition should not improve the model (compared to a model that has a single drift rate parameter for all word stimuli regardless of priming condition) , while
\item
  allowing the non-decision parameter \(T_{er}\) to vary as a function of the priming conditions for word stimuli should improve the model (compared to a model that has only one \(T_{er}\) parameter for all word stimuli regardless of priming condition).
\end{enumerate}

@@

\begin{enumerate}
\def\labelenumi{\alph{enumi})}
\item
  allowing the drift rate parameter for words to vary as a function of the priming condition should improve the model compared to a model that has a single drift rate parameter for all word stimuli regardless of priming condition, and
\item
  allowing the non-decision parameter \(T_{er}\) to vary as a function of the priming conditions for word stimuli should improve the model compared to a model that has only one \(T_{er}\) parameter for all word stimuli regardless of priming condition.
\end{enumerate}

@@

\hypertarget{experiment-1}{%
\section{Experiment 1}\label{experiment-1}}

In the first experiment, we tested whether we could observe reliable effects of masked priming at prime durations of 33 ms and 50 ms (roughly corresponding to two and three frames at a refresh rate of 60 Hz).

@@

\hypertarget{method}{%
\subsection{Method}\label{method}}

\begin{verbatim}
## Warning: package 'sp' was built under R version 4.0.4
\end{verbatim}

\begin{verbatim}
## Warning: package 'rworldmap' was built under R version 4.0.4
\end{verbatim}

\hypertarget{participants}{%
\subsubsection{Participants}\label{participants}}

We collected data from 78 participants aged from 18 to 99 (mean age: 31.94) recruited through Prolific (www.prolific.co, Prolific (2021)). The experiment was only be shown to participants who have indicated that English is their first language in the Prolific screening questions. They were paid £1.25 for their participation (corresponding to £5/hour). Participants indicated that English was their first language before starting the experiment.

\hypertarget{material}{%
\subsubsection{Material}\label{material}}

\hypertarget{procedure}{%
\subsubsection{Procedure}\label{procedure}}

\hypertarget{data-analysis}{%
\subsubsection{Data analysis}\label{data-analysis}}

@@

\hypertarget{results}{%
\subsection{Results}\label{results}}

\hypertarget{discussion}{%
\subsection{Discussion}\label{discussion}}

\hypertarget{general-discussion}{%
\section{General Discussion}\label{general-discussion}}

@@

\leavevmode\hypertarget{ref-prolific2021}{}%
Prolific. (2021). Prolific \textbar{} online participant recruitment for surveys and market research. Retrieved from \url{https://www.prolific.co/}
